Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2017-02-07 Manuscript/Manuscript_using_actual_data.Rmd
forget what i did

**Figure 5a: Trends in life expectancy for white males between 1969 and 2013 by US state**

```{r figure5a, fig.align="center", fig.height=4, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

```{r figure5b, fig.align="center", fig.height=4, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_black, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

```{r figure5c, fig.align="center", fig.height=4, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_wbgap, x = year)) + 
           geom_vline(aes(xintercept = 1983), lty = 2, lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), lty = 2, lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_wbgap_lcl, ymax = LE_wbgap_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

**Figure 6a: Contribution of cancer to the black-white life expectancy gap for males between 1969 and 2013 by US state, in years**
```{r figure6a, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cancers"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap(~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

**Figure 6a (ii): Contribution of cancer (%) to the black-white life expectancy gap for males between 1969 and 2013 by US state**
```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cancers"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap(~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cardiovascular"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap(~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cardiovascular"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cardiovascular"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cardiovascular"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Communicable"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Communicable"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Non-communicable"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Non-communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Non-communicable"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Non-communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Injuries"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Injuries"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Injuries"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Injuries"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

**Figure 6f: Contribution of all other causes to the black-white life expectancy gap for males between 1969 and 2013 by US state, in years**
```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "All other causes"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "All other causes"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "All other causes"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "All other causes"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=4, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r, fig.align="center", fig.height=4, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_black, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

```{r figure6, fig.align="center", fig.height=4, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_wbgap, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_wbgap_lcl, ymax = LE_wbgap_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), aes(label = stabbrs), check_overlap = T, size = 2.5) 
) 
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Cancers"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Cancers"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

**Figure 8b: Contribution of cardiovascular disease to the black-white life expectancy gap for females between 1969 and 2013 by US state, in years**
```{r,  fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Cardiovascular"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Cardiovascular"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)

@@

**Figure 8c: Contribution of communicable disease to the black-white life expectancy gap for females between 1969 and 2013 by US state, in years**
```{r,  fig.align="center", fig.height=5, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Communicable"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)

>>>>

**Figure 5a: Trends in life expectancy for white males between 1969 and 2013 by US state**
```{r jitter, echo=F}
BlackWhite_results$jitter_year <- sample(x= c(2008:2013), length(BlackWhite_results$year), replace = T)
```

```{r figure5a, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

```{r figure5b, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_black, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

```{r figure5c, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_wbgap, x = year)) + 
           geom_vline(aes(xintercept = 1983), lty = 2, lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), lty = 2, lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_wbgap_lcl, ymax = LE_wbgap_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

**Figure 6a: Contribution of cancer to the black-white life expectancy gap for males between 1969 and 2013 by US state, in years**
```{r figure6a, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cancers"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap(~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

**Figure 6a (ii): Contribution of cancer (%) to the black-white life expectancy gap for males between 1969 and 2013 by US state**
```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cancers"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap(~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cardiovascular"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap(~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cardiovascular"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Cardiovascular"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Cardiovascular"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Communicable"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Communicable"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Non-communicable"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Non-communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Non-communicable"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Non-communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Injuries"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Injuries"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "Injuries"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "Injuries"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

**Figure 6f: Contribution of all other causes to the black-white life expectancy gap for males between 1969 and 2013 by US state, in years**
```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "All other causes"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "All other causes"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & COD == "All other causes"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Male" & COD == "All other causes"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_black, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

```{r figure6, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_wbgap, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_wbgap_lcl, ymax = LE_wbgap_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), aes(label = stabbrs), check_overlap = T, size = 2.5) 
) 
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Cancers"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r, fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Cancers"), aes(x = year, y = COD_cont_prop)) + 
           geom_ribbon(aes(ymin = COD_cont_prop_lcl, ymax = COD_cont_prop_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (%)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Cancers"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

**Figure 8b: Contribution of cardiovascular disease to the black-white life expectancy gap for females between 1969 and 2013 by US state, in years**
```{r,  fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Cardiovascular"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Cardiovascular"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)

@@

**Figure 8c: Contribution of communicable disease to the black-white life expectancy gap for females between 1969 and 2013 by US state, in years**
```{r,  fig.align="center", fig.height=9, fig.width=11, echo=F}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & COD == "Communicable"), aes(x = year, y = COD_cont_yrs)) + 
           geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) + facet_wrap( ~ Census_Division, ncol = 3) +
           ylab("Contribution to LE Gap (years)") +
           xlab("Year") +
           geom_text(data = subset(cod_decomp_results, year == 2013 & sex == "Female" & COD == "Communicable"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5)
)
